### 2013-02-16 doc/icml2013/algo.tex

\begin{theorem}[Convergence of Spectral Experts]
  \label{thm:convergence}
Each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d. points drawn from the mixture
of linear regressions model with parameter $\theta^*$
(having three independent copies simplifies the analysis).
Let $\|x\|_2 \le R$ with probability $1$
and let $\|\beta_h^*\|_2 \le L$ for all $h \in [k]$.
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$, 
and assume $\Sigma_p \succ 0$ for each $p \in \{1,2,3\}$.
Assume $d \ge k$.
Suppose the number of samples is
$n = \max(n_1,n_2)$
where $n_1 = \Omega(d^p R^p \sigmamin(\Sigma_p)^{-1} \sqrt{p \log(d) \log(1/\delta)})$ and
$n_2 = \Omega\left( \sigma^6 L^6 R^12 k \sigmamin(\Sigma_p)^{-2} \frac{\log^3 (1/\delta)}{\epsilon^2} \right)$.
If the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$ are
set to $\Omega(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}})$,
then the parameter estimates $\hat\theta = (\hat\pi, \hat B)$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriate permuted)
satisfies 
$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
and for all $h \in [k]$,
$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\pi_h^*}$.
\end{theorem}

>>>>

\begin{theorem}[Convergence of Spectral Experts]
  \label{thm:convergence}
Each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d. points drawn from the mixture
of linear regressions model with parameter $\theta^*$
(having three independent copies simplifies the analysis).
Let $\|x\|_2 \le R$ with probability $1$
and let $\|\beta_h^*\|_2 \le L$ for all $h \in [k]$.
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$, 
and assume $\Sigma_p \succ 0$ for each $p \in \{1,2,3\}$.
Assume $d \ge k$.
Suppose the number of samples is
$n = \max(n_1,n_2)$
where $n_1 = \Omega(d^p R^p \sigmamin(\Sigma_p)^{-1} \sqrt{p \log(d) \log(1/\delta)})$ and
$n_2 = \Omega\left( \sigma^6 L^6 R^{12} k \sigmamin(\Sigma_p)^{-2} \frac{\log^3 (1/\delta)}{\epsilon^2} \right)$.
If the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$ are
set to $\Omega(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}})$,
then the parameter estimates $\hat\theta = (\hat\pi, \hat B)$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriate permuted)
satisfies 
$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
and for all $h \in [k]$,
$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\pi_h^*}$.
\end{theorem}
